API design for machine learning software: experiences from the scikit-learn project

### 2013-09-11 paper.tex
figures at top of page
Makes the footnotes come out better.

\begin{figure*}[b]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA

union = FeatureUnion([("pca", PCA()),
                      ("kpca", KernelPCA(kernel="rbf"))])

Pipeline([("feat_union", union),
          ("log_reg", LogisticRegression(penalty="l2"))
         ]).fit(X_train, y_train)
\end{pythoncode}
\caption{A union of linear PCA and kernel PCA for feature extraction.}
\label{pca-union}
\end{figure*}

@@

\begin{figure*}[b]
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.svm import SVC

>>>>

\begin{figure*}[t]
\begin{pythoncode}
from sklearn.pipeline import FeatureUnion, Pipeline
from sklearn.decomposition import PCA, KernelPCA

union = FeatureUnion([("pca", PCA()),
                      ("kpca", KernelPCA(kernel="rbf"))])
Pipeline([("feat_union", union),
          ("log_reg", LogisticRegression(penalty="l2"))
         ]).fit(X_train, y_train)
\end{pythoncode}
\caption{A union of linear PCA and kernel PCA for feature extraction.}
\label{pca-union}
\end{figure*}

@@

\begin{figure*}[t]
\begin{pythoncode}
from sklearn.grid_search import GridSearchCV
from sklearn.svm import SVC
